---
title: "Replication of R components"
output: github_document
---

# Setup

First, load up the necessary packages. We are operating in interactive mode, so `{{tidyverse}}` can be used and is inclusive of `{{ggplot2}}`, `{{scales}}`, and `{{dplyr}}`.

```{r load packages}
library(readstata13)
library(psych)
library(tidyverse)
library(scales)
library(gt)
library(pander)
```

We don't need to set paths, and assume folks will follow the practice of using an RStudio project with the project folder as the main parent folder. All paths are thus local to that.

```{r set data paths}
datafile_survey_1 <- here::here("data", "MasterFile_Survey1.dta")
datafile_survey_2 <- here::here("data", "Online_Data_Survey2.dta")
```

# Survey 1 (German Internet Panel)

## Read in data

```{r load data}
# load data - labels will be lost
df_study1 <- read.dta13(file = datafile_survey_1, 
                        convert.factors = TRUE, 
                        nonint.factors = TRUE)
```

## Recoding

```{r}
dat_study1 <- df_study1 %>%
    rename(priming = rich) %>%
    mutate(priming = case_match(priming, 
                                0 ~ "primed poor", 
                                1 ~ "primed rich"), 
           income = round(income * 1000), 
           male = male * 100, 
           married = married * 100, 
           student = student * 100, 
           east = east * 100, 
           manip = gsub("[0-9]+\\.\\s+([0-9]+)", "\\1", manip) %>%
               as.numeric())
```

## Generate Table 1 (sample summary statistics - survey 1)
```{r, results = "asis"}
summary_vars <- c("income", "male", "age", "edu", "married", 
                  "student", "religiousness", "east", "leftright")

# define function to count number of not NA values
obs <- function(x, na.rm) {sum(is.finite(x))}

# define function to create summary table
make_summary_table <- function(df, vars = summary_vars)
{
    summarize_at(df, vars, 
                 list(obs = obs, mean = mean, sd = sd), na.rm = TRUE) %>%
    pivot_longer(cols = everything(), 
                 names_to = c("set", ".value"), 
                 names_pattern = "(.+)_([a-z]+)")
}

# generate separate tables for primed poor and primed rich
dat_rich <- dat_study1 %>%
    filter(priming == "primed rich")

dat_poor <- dat_study1 %>%
    filter(priming == "primed poor")

summary_rich <- make_summary_table(dat_rich)
summary_poor <- make_summary_table(dat_poor)
summary_out <- left_join(summary_rich, summary_poor, by = "set", 
                         suffix = c("", ".")) %>%
    mutate_at(vars(-"set"), ~(round(., digits = 1))) %>%
    rename(variable = set)
```

## Wilcox-Rank-Sum tests for Table 1 

```{r summary tests survey 1}
U_test <- function(var, df1 = dat_rich, df2 = dat_poor)
{
    wilcox.test(x = df1[[var]], 
                y = df2[[var]], 
                paired = FALSE)
}

stats <- tibble(variable = summary_vars, 
             results = map(variable, U_test), 
             p_value = map_dbl(results, pluck, "p.value"))

p_cutoffs <- c(0.1, 0.05, 0.01)
```

## Table 1

```{r table 1, results = "asis"}
table_1 <- summary_out %>%
    mutate(mean = paste(pander::add.significance.stars(stats$p_value, 
                                                        cutoffs = p_cutoffs), mean)) %>% 
    gt() %>%
    tab_spanner(label = "primed rich",
                columns = c("obs", "mean", "sd")) %>%
    tab_spanner(label = "primed poor",
                columns = c("obs.", "mean.", "sd.")) %>%
    cols_align(align = "right", "mean")

table_1 %>% as_raw_html()
```

Stars (`*`, `* *`, `* * *`) indicate significance (between the rich and poor conditions) at the `r p_cutoffs` levels, respectively.

```{r table 1 tex output}
table_1 %>% as_latex() %>% write_lines(file = here::here("tex", "table_1.tex"))
```

## Figure 2

```{r}
#| fig.cap = "Histogram of Individual Payments"
    
ggplot(dat_study1) + 
    aes(x = payment, y = ..ncount.. / sum(..ncount..)) + 
    geom_histogram(bins = 11, color = "black") + 
    geom_hline(yintercept = 1/11, linetype = "dashed") + 
    scale_y_continuous(labels = percent_format()) + 
    theme_bw()
```

## Figure A1.1

To create figure A1.1, convert income into a factor variable with proper labels, then generate counts, and plot the data.

```{r}
income_labels <- c("less than 150 Euro",
                   "150 to less than 400 Euro",
                   "400 to less than 1000 Euro",
                   "1000 to less than 1500 Euro",
                   "1500 to less than 2000 Euro",
                   "2000 to less than 2500 Euro",
                   "2500 to less than 3000 Euro",
                   "3000 to less than 3500 Euro",
                   "3500 to less than 4000 Euro",
                   "4000 to less than 4500 Euro",
                   "4500 to less than 5000 Euro",
                   "5000 to less than 5500 Euro",
                   "5500 to less than 6000 Euro",
                   "5000 to less than 7500 Euro",
                   "7500 Euro and more")

plot_randomization_by_income <- function(to_plot, counts)
{
    to_plot %>%
    ggplot(aes(x = income, group = priming)) + 
    geom_bar(aes(fill = priming), position = "fill") + 
    geom_text(data = counts, aes(y = pos, label = n)) + 
    coord_flip() + 
    theme_bw() + 
    ylab("Proportion") + xlab("Income Group")
}

to_plot <- dat_study1 %>%
    mutate(income = factor(income, labels = income_labels))

counts <- to_plot %>%
    count(income, priming) %>%
    mutate(pos = case_when(priming == "primed poor" ~ 0.9,
                           priming == "primed rich" ~ 0.1))

plot_randomization_by_income(to_plot, counts)
```

## Figure A2.1

Manipulation Check (y-axis) vs Income, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group <- function(df, var, group = income)
{
    df %>%
        filter(priming %in% c("primed rich", "primed poor")) %>%
        group_by({{group}}, priming) %>%
        summarize("{{var}}" := mean({{var}}, na.rm = TRUE), 
                  .groups = "drop") %>% 
        mutate(priming = fct_relevel(priming, c("primed rich", "primed poor"))) %>%
        ggplot(aes(x = {{group}}, y = {{var}}, 
                   fill = priming, color = priming, shape = priming)) + 
        geom_point(size = 2) + 
        scale_shape_manual(values = c(19, 23)) + 
        scale_fill_manual(values = c("black", "grey80")) + 
        scale_color_manual(values = c("black", "grey80")) + 
        theme_bw()
}
```

```{r}
plot_var_vs_group(dat_study1, manip) + 
    scale_x_continuous(breaks = seq(from = 1000, to = 9000, by = 1000)) + 
    scale_y_continuous(limits = c(4, 8))
```

## Figure A3.1

Payments vs. Income, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study1, payment) + 
    scale_x_continuous(breaks = seq(from = 1000, to = 9000, by = 1000)) + 
    scale_y_continuous(limits = c(6, 14))
```

## Figure A4.1

Payments vs. Age, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study1, payment, age) + 
    scale_x_continuous(breaks = seq(from = 17, to = 82, by = 10)) + 
    scale_y_continuous(limits = c(6, 16))
```

## Figure A4.3

Payments vs. Education, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study1, payment, edu) + 
#    scale_x_continuous(breaks = seq(from = 17, to = 82, by = 10)) + 
    scale_y_continuous(limits = c(6, 16))
```

# Survey 2

## Read in data

```{r load data 2}
# load data - labels will be lost
df_study2 <- read.dta13(file = datafile_survey_2, 
                        convert.factors = TRUE, 
                        nonint.factors = TRUE)
```

## Recoding

```{r recode data 2}
dat_study2 <- df_study2 %>%
    mutate(income = case_match(q37, 
                               1 ~ 75, 
                               2 ~ 275, 
                               3 ~ 700, 
                               4 ~ 1250, 
                               5 ~ 1750, 
                               6 ~ 2250, 
                               7 ~ 2750, 
                               8 ~ 3250, 
                               9 ~ 3750, 
                               10 ~ 4250, 
                               11 ~ 4750, 
                               12 ~ 5250, 
                               13 ~ 5750, 
                               14 ~ 6750, 
                               15 ~ 0, 
                               .default = NA) + 
               case_match(q38, 
                          1 ~ 8750, 
                          2 ~ 12500, 
                          3 ~ 17500, 
                          4 ~ 25000, 
                          .default = 0), 
           male = case_match(q7, 
                             1 ~ 100, 
                             2 ~ 0, 
                             .default = 0), 
           age = 88 - q8*5, 
           edu = case_match(q10, 
                            7 ~ 4, 
                            .default = q10), 
           married = case_match(q12, 
                                1 ~ 100, 
                                .default = 0), 
           student = case_match(q11, 
                                1 ~ 100, 
                                .default = 0), 
           religiousness = q13, 
           east = as.numeric(substr(df_study2$q31, 1, 1) < 2) * 100,
           leftright = q14, 
           priming = case_match(treatment, 
                                "Primed_poor" ~ "primed poor", 
                                "Primed_rich" ~ "primed rich", 
                                .default = "control"), 
           manip = 11 - select(., q4_1:q4_10) %>%
               mutate_all(~. == "On") %>%
               as.matrix() %>%
               apply(1, which), 
           payment = payoff)
```

## Generate Table 2 (sample summary statistics - survey 1)
```{r summary table 2, results = "asis"}
summary_vars <- c("income", "male", "age", "edu", "married", 
                  "student", "religiousness", "east", "leftright")


# generate separate tables for primed poor and primed rich
dat_rich <- dat_study2 %>% filter(priming == "primed rich")
dat_poor <- dat_study2 %>% filter(priming == "primed poor")
dat_control <- dat_study2 %>% filter(priming == "control")

summary_rich <- make_summary_table(dat_rich)
summary_poor <- make_summary_table(dat_poor)
summary_control <- make_summary_table(dat_control)
summary_out <- summary_rich %>%
    left_join(summary_poor, by = "set", 
              suffix = c("", ".")) %>%
    left_join(summary_control, by = "set", 
              suffix = c("", "..")) %>%
    mutate_at(vars(-"set"), ~(round(., digits = 1))) %>%
    rename(variable = set)
```

## Wilcox-Rank-Sum tests for Table 2

```{r summary tests survey 2}
p_cutoffs <- c(0.1, 0.05, 0.01)

stats <- tibble(variable = summary_vars, 
             results_rich_control = map(variable, U_test, dat_rich, dat_control),
             results_poor_control = map(variable, U_test, dat_poor, dat_control),
             results_rich_poor = map(variable, U_test, dat_rich, dat_poor), 
             p_value_rich_control = map_dbl(results_rich_control, pluck, "p.value"), 
             p_value_poor_control = map_dbl(results_poor_control, pluck, "p.value"), 
             p_value_rich_poor = map_dbl(results_rich_poor, pluck, "p.value"), 
             stars_rich_control = pander::add.significance.stars(p_value_rich_control,
                                                                 cutoffs = p_cutoffs), 
             stars_poor_control = pander::add.significance.stars(p_value_poor_control,
                                                                 cutoffs = p_cutoffs), 
             stars_rich_poor = gsub("\\*", "†", 
                                    pander::add.significance.stars(p_value_rich_poor,
                                                                 cutoffs = p_cutoffs)))
```

## Table 2

```{r table 2, results = "asis"}
summary_out %>%
    mutate(mean = paste(stats$stars_rich_control, stats$stars_rich_poor, mean), 
           `mean.` = paste(stats$stars_poor_control, `mean.`)) %>% 
    gt() %>%
    tab_spanner(label = "primed rich", 
                columns = c("obs", "mean", "sd")) %>%
    tab_spanner(label = "primed poor", 
                columns = c("obs.", "mean.", "sd.")) %>%
    tab_spanner(label = "control", 
                columns = c("obs..", "mean..", "sd..")) %>%
    as_raw_html()
```

Stars (`*`, `* *`, `* * *`) indicate significance (between the rich and control OR between the poor and control conditions) at the `r p_cutoffs` levels, respectively. Daggers (`†`, `† †`, `† † †`) indicate significance (between the rich and poor conditions) at the `r p_cutoffs` levels, respectively. 

## Figure A1.2

To create figure A1.2, convert income into a factor variable with proper labels, then generate counts, and plot the data.

```{r}
to_plot <- dat_study2 %>%
    mutate(income = factor(q37, labels = income_labels))

counts <- to_plot %>%
    count(income, priming) %>%
    mutate(pos = case_when(priming == "primed poor" ~ 0.5,
                           priming == "primed rich" ~ 0.1, 
                           .default = 0.9))

plot_randomization_by_income(to_plot, counts)
```

## Figure A2.2

Manipulation Check (y-axis) vs Income, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study2, manip) + 
    scale_x_continuous(breaks = seq(from = 5000, to = 25000, by = 5000)) + 
    scale_y_continuous(breaks = 4:10)
```

## Figure A3.2

Payments vs. Income, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study2, payment) + 
    scale_x_continuous(breaks = seq(from = 5000, to = 25000, by = 5000)) + 
    scale_y_continuous(limits = c(6, 16))
```

The labels appear reversed from Figure A3.2 in the appendix. Let's check with the raw values for the income == 17,500 group. Note the income filter is based on the coding scheme in file `Supplementary-Survey2.Rmd` in the replication package.

```{r}
dat_subset <- df_study2 %>% 
    filter(q37==15, q38==3) %>% # income filter
    select(q37, q38, treatment, payoff) %>%
    arrange(treatment)

knitr::kable(dat_subset)
```

So the `Primed_poor` group has an average payoff of `r dat_subset %>% filter(treatment == "Primed_poor") %>% pull(payoff) %>% mean()` and the `Primed_rich` has an average payoff of `r dat_subset %>% filter(treatment == "Primed_rich") %>% pull(payoff) %>% mean()`.

This matches our replication figure, which indeed has reversed labels from the appendix figure A3.2.

## Figure A4.2

Payments vs. Age, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study2, payment, age) + 
    scale_x_continuous(breaks = seq(from = 17, to = 82, by = 10)) + 
    scale_y_continuous(limits = c(6, 16))
```

## Figure A4.4

Payments vs. Education, grouped by "Primed-Rich" and "Primed-Poor"

```{r}
plot_var_vs_group(dat_study2, payment, edu) + 
#    scale_x_continuous(breaks = seq(from = 17, to = 82, by = 10)) + 
    scale_y_continuous(limits = c(6, 16))
```
